Bibat: Batteries-include Bayesian Analysis Template

### 2024-04-05 paper/main.qmd

---
title: "Bibat: Batteries-include Bayesian Analysis Template"
abstract: >
  Bayesian statistical workflow offers a powerful way to learn from data,
  but software software projects that implement complex Bayesian workflows
  in practice are unusual, partly due to the difficulty of orchestrating
  Bayesian statistical software. Bibat addresses this challenge by providing
  a full-featured, scalable Bayesian statistical analysis project using
  an interactive template. Bibat is available on the Python Package index,
  documented at <https://bibat.readthedocs.io/> and developed at <https://github.com/teddygroves/bibat/>. Bibat is free to use under the MIT license. This paper explains the motivation for bibat, describes intended usage, discusses bibat's design, compares bibat with similar software, highlights several examples of bibat's use in science and provides links to community resources associated with bibat.
number-sections: true
author:
  - name: "Teddy Groves"
    orcid: 0000-0002-7109-3270
    email: tedgro@biosustain.dtu.dk
    affiliations:
      - id: 1
        name: Danish Technical University
        department: The Novo Nordisk Foundation Center for Biosustainability
        city: Kongens Lyngby
        country: Denmark
    attributes:
      corresponding: true
bibliography: bibliography.bib
keywords: [Bayesian workflow, Methodology, Software]
format:
  html:
    embed-resources: true
  pdf:
    template: automl-template.tex
    template-partials:
      - title.tex
---

>>>>

---
title: "Bibat: Batteries-include Bayesian Analysis Template"
abstract: >
  Bayesian statistical workflow offers a powerful way to learn from data,
  but software projects that implement complex Bayesian workflows
  in practice are unusual, partly due to the difficulty of orchestrating
  Bayesian statistical software. Bibat addresses this challenge by providing
  a full-featured, scalable Bayesian statistical analysis project using
  an interactive template. Bibat is available on the Python Package index,
  documented at <https://bibat.readthedocs.io/> and developed at <https://github.com/teddygroves/bibat/>. Bibat is free to use under the MIT license. This paper explains the motivation for bibat, describes intended usage, discusses bibat's design, compares bibat with similar software, highlights several examples of bibat's use in science and provides links to community resources associated with bibat.
number-sections: true
author:
  - name: "Teddy Groves"
    orcid: 0000-0002-7109-3270
    email: tedgro@biosustain.dtu.dk
    affiliations:
      - id: 1
        name: Danish Technical University
        department: The Novo Nordisk Foundation Center for Biosustainability
        city: Kongens Lyngby
        country: Denmark
    attributes:
      corresponding: true
bibliography: bibliography.bib
keywords: [Bayesian workflow, Methodology, Software]
format:
  html:
    embed-resources: true
  pdf:
    template: automl-template.tex
    template-partials:
      - title.tex
---
